What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-27 paper/main.tex
fixed bib file

\section{Conclusion}
The Achilles heel of formal verification is specification; formal methods are only as effective at verification as their specifications are at describing the essential properties to verify. Yet, specification remains the biggest bottleneck to the use of formal methods~\cite{Roz16}. \ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
 %
Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that \ltl\ formulas capture the specifications they are meant to capture. A major contributor to \ltl's popularity is the propensity of humans to think of requirements in terms of timelines. This inspired the creation of \ltl\ in the first place, as a logic that ``intuitively'' represents timelines. Our work serves to reinforce that connection, enabling visualization of most realistic \ltl\ formulas as timelines. By releasing \tool, we contribute to better validation capabilities for \ltl\ specifications and aid the effort to make formal verification more accessible and wide-spread.
%We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.

>>>>

\section{Conclusion}
The Achilles heel of formal verification is specification; formal methods are only as effective at verification as their specifications are at describing the essential properties to verify. Yet, specification remains the biggest bottleneck to the use of formal methods~\cite{Roz16}. \ltl\ is one of the most popular specification logics for industrial-scale critical systems; in the space domain alone, it is currently encapsulating specifications for the development of the NASA Lunar Gateway~\cite{DBR21,DBR23}, the Air Force Research Laboratory/Collins Aerospace Spacecraft Collision Avoidance system~\cite{HDWF21}, Space Systems Finland's Attitude and Orbit Control Systems (AOCS)~\cite{ILLTV13}, and NASA/JPL's Europa Lander Mission Concept~\cite{CDRWRWL22} just to name a few.
 %
Yet the humans that need to use formal verification tools and deeply understand their results struggle to validate that \ltl\ formulas capture the specifications they are meant to capture. A major contributor to \ltl's popularity is the propensity of humans to think of requirements in terms of timelines. This inspired the creation of \ltl\ in the first place, as a logic that ``intuitively'' represents timelines. Our work serves to reinforce that connection, enabling visualization of most realistic \ltl\ formulas as timelines. By releasing \tool, we contribute to better validation capabilities for \ltl\ specifications and aid the effort to make formal verification more accessible and wide-spread.
%We hope that this will assist system designers in formulating error-free specifications and thus improve the effectiveness of verification tools for \ltl.
